---
title: "Hoffmann Dataset"
fontsize: 10pt
output:
  pdf_document:
    df_print: kable
    latex_engine: xelatex
    number_sections: yes
    toc: yes
    toc_depth: 2
    highlight: tango
    fig_caption: yes
geometry: "left=0.5in, right=0.5in, top=1in, bottom=1in"
urlcolor: blue
always_allow_html: true
header-includes:
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{placeins}
  - \usepackage[T1]{fontenc}    
  - \usepackage{xcolor}
  - \setmainfont{Arial}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format = "latex")
```

```{r library, include=FALSE}
library(tidyverse)
library(ggplot2)  
library(rmarkdown)  
library(markdown)  
library(kableExtra)
```

\vspace{36pt}  
Disclaimer: I did not create or collect data to compile this dataset.

For more details about the dataset and the creators, Ralf Lichtinghagen, Frank Klawonn, and Georg Hoffmann, please visit:
https://archive.ics.uci.edu/ml/datasets/HCV+data.


\pagebreak
# Summary # 

For **Category**, there are 5 different classifications which includes the stages of Hep C:
*0=Blood Donor, 0s=suspect Blood Donor, 1=Hepatitis, 2=Fibrosis, 3=Cirrhosis.*

There are 10 different labs taken from each patient. The labs include: albumin (**ALB**), bilirubin (**BIL**), choline esterase (**CHE**), $\gamma$-glutamyl-transferase (**GGT**), aspartate amino-transferase (**AST**), and alanine amino-transferase (**ALT**).


```{r dataset, echo=FALSE}

HCV_data <- kable(old_HCV, align = "c", escape = T) %>%
  kableExtra::kable_styling(latex_options = c("hold_position", "striped"),
                            stripe_color = "#DADADA",
                            font_size = 8) %>%
  row_spec(0,
           color = "#FFFFFF",
           background = "#3E7DCC",
           bold = T) %>%
  column_spec(1, border_left = T) %>%
  column_spec(ncol(old_HCV), border_right = T)
```
\renewcommand{\arraystretch}{2}
\begin{center}
`r HCV_data`
\end{center}

\pagebreak
# Patient Demographics # 

## Age Range ##

```{r Demographics-1, echo=FALSE, fig.align='center', fig.cap='The number of patients in each age interval'}
plot1
```






